Generalized Tractability

### 2023-04-21 GeneralizedTractability_230418.tex
Fred M2 2023 Mac Updates

We make the technical assumption that $\SOL_d$ is a compact operator. This implies (see, e.g., \cite{NW08}) that $\lambda_{i,d}$ converges to zero as $i$ tends to infinity for every $d$, which in turn implies that the problem is solvable by suitable algorithms. To avoid trivial cases, we assume that there are an infinite number of positive eigenvalues.

@@

The information complexity of the problem $\SOL_d$ is given by the function $\comp:(0,\infty) \times \naturals \to \natzero$, where $\comp(\varepsilon,d)$ is the minimum number of linear functionals required to satisfy the error criterion \eqref{eq:errcrit}.
By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.  We also expect it to be non-decreasing as $d$ tends to infinity, since $d$ is typically the number of variables for the functions in $\cf_d$.

>>>>

We make the technical assumption that $\SOL_d$ is a compact operator. This implies (see, e.g., \cite{NW08}) that $\lambda_{i,d}$ converges to zero as $i$ tends to infinity for every $d$, which in turn implies that the problem is solvable by suitable algorithms. To avoid trivial cases, we assume that there are an infinite number of positive eigenvalues for every $d$.

@@

The information complexity of the problem $\SOL_d$ is given by the function $\comp:(0,\infty) \times \naturals \to \natzero$, where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best algorithm to satisfy the error criterion \eqref{eq:errcrit}.
By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.  We also expect it to be non-decreasing as $d$ tends to infinity, since $d$ is typically the number of variables for the functions in $\cf_d$.
